Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-25 ICLR25/experiments.tex
clean up

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=61$}&\multicolumn{2}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-6}
		\text{$|X|$}  & \text{Random} & \cite{ DivideAndSlide} & \bf Utility& \text{Random} &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729&  \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 & \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l||c|c|c||c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & \bf Hybrid \\ 
		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & \bf MILP \\ 
		\hline
		MNIST 5$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
		(92s) & 13\% \bf (46s) \\ \hline
		MNIST 5$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
		MNIST 8$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
		MNIST 8$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & N/A & 
		\bf 10\% (402s) \\ \hline
		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & N/A & \bf 11\% (417s) \\ \hline \hline
		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & N/A & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}), TO UPDATE.}
	\label{table_hybrid}
	\end{table}

@@

We volontarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much cluter.

Notice that results for several other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with defavorable comparison vs $\alpha,\beta$-CROWN. Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd 
of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN. Concerning MnBAB \cite{ferrari2022complete}, it compares slightly defavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv \cite{ferrari2022complete}, and we also run it for the MNIST DNNs, and it was slightly slower and less accurate than $\alpha,\beta$-CROWN at several time-out settings. 
Last, Pyrat code (2sd in the latest VNNComp) is not open source, which made running it impossible.

>>>>

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c||c|c|}
		\hline
			&\multicolumn{3}{c||}{$X \subseteq$ Layer 2, max $=61$}&\multicolumn{2}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-6}
		\text{$|X|$}  & \text{Random} & \cite{ DivideAndSlide} & \bf Utility& \text{Random} &\bf Utility\\ \hline
		\hline
		0  (LP) &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline \hline
		5  &   1.729&1.704 & 1.603&  1.729&  \bf 1.532 \\ \hline
		10  &  1.701 &  1.651 &1.517& 1.696 & \bf  1.371\\ \hline
		15  & 1.671 &  1.599 &1.466&  1.653& \bf  1.247\\ \hline
		20  &  1.635 & 1.557&1.438 & 1.619 & \bf  1.145\\ \hline
		25  &  1.601 & 1.519 &1.427&  1.586 & \bf 1.061\\ \hline
		30  & 1.574 & 1.489 &1.425& 1.546 & \bf  0.989 \\ \hline
		35  &  1.542 & 1.465&1.424 & 1.502 & \bf 0.934 \\ \hline
		40  & 1.512 & 1.447 &1.424& 1.469 & \bf 0.921 \\ \hline \hline
		max & 1.424  &1.424& 1.424 & 0.895 & 0.895   \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{tab:example1}
	%\vspace{-0.6cm}
\end{table}

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l||c|c|c||c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & \bf Hybrid \\ 
		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & \bf MILP \\ 
		\hline
		MNIST 5$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
		(92s) & 13\% \bf (46s) \\ \hline
		MNIST 5$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
		MNIST 8$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
		MNIST 8$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & $-$ & 
		\bf 10\% (402s) \\ \hline
		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}) as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown and Hybrid MILP on 7 DNNs (average runtime per image). The 6 first DNNs are hard instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
	\label{table_hybrid}
	\end{table}

@@

We voluntarily limited the comparison to $\alpha,\beta$-Crown because it is the most efficient verifier available to date, and it enabled us to consider a spectre of parameters to understand $\alpha,\beta$-Crown scaling without too much clutter.

Notice that results for several other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN. Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd 
of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN. Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings. Last, Pyrat code (2sd in the latest VNNComp) is not open source, which made running it impossible.
